R Notebook

### 2019-10-16 src/plots for paper.Rmd
2d plots finished

```{r pre-install & load packages, include=FALSE}
packages <- c("stringr", "reshape2", "ggplot2", "Hmisc", "viridis", "raster", "RColorBrewer", "cowplot")
source("../src/ipak.R")
ipak(packages)
```

@@

the maps need to be layered with the land etc, trimmed, and coloured to whatever is agreed

with rastervis

>>>>

```{r pre-install & load packages, include=FALSE}
packages <- c("stringr", "reshape2", "ggplot2", "Hmisc", "viridis", "raster", "RColorBrewer", "cowplot", "rasterVis")
source("../src/ipak.R")
ipak(packages)
```

@@

now create summary maps where values are binary - not counts of cells
```{r}
binprob <- function(x){
  ifelse(x > 0, 1,
  ifelse(x <= 0, 0, NA))
}

  clogasc_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = "*_bin_0.5_2d.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
```

then plot the maps

s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
ss <- raster::intersect(s, mcp)  #trim to mcp

mar2d <- raster("../output/maxent/paper_plots/hotspot_mapping/mar_bin_0.5_2d_single.asc")
apr2d <- raster("../output/maxent/paper_plots/hotspot_mapping/apr_bin_0.5_2d_single.asc")
may2d <- raster("../output/maxent/paper_plots/hotspot_mapping/may_bin_0.5_2d_single.asc")
jun2d <- raster("../output/maxent/paper_plots/hotspot_mapping/jun_bin_0.5_2d_single.asc")
jul2d <- raster("../output/maxent/paper_plots/hotspot_mapping/jul_bin_0.5_2d_single.asc")
aug2d <- raster("../output/maxent/paper_plots/hotspot_mapping/aug_bin_0.5_2d_single.asc")
sep2d <- raster("../output/maxent/paper_plots/hotspot_mapping/sep_bin_0.5_2d_single.asc")
oct2d <- raster("../output/maxent/paper_plots/hotspot_mapping/oct_bin_0.5_2d_single.asc")
nov2d <- raster("../output/maxent/paper_plots/hotspot_mapping/nov_bin_0.5_2d_single.asc")
dec2d <- raster("../output/maxent/paper_plots/hotspot_mapping/dec_bin_0.5_2d_single.asc")

#trim to mcp
mar2d <- raster::mask(mar2d, mcp)
apr2d <- raster::mask(apr2d, mcp)
may2d <- raster::mask(may2d, mcp)
jun2d <- raster::mask(jun2d, mcp)
jul2d <- raster::mask(jul2d, mcp)
aug2d <- raster::mask(aug2d, mcp)
sep2d <- raster::mask(sep2d, mcp)
oct2d <- raster::mask(oct2d, mcp)
nov2d <- raster::mask(nov2d, mcp)
dec2d <- raster::mask(dec2d, mcp)

#add crs
mar2d@crs <- acrs
apr2d@crs <- acrs
may2d@crs <- acrs
jun2d@crs <- acrs
jul2d@crs <- acrs
aug2d@crs <- acrs
sep2d@crs <- acrs
oct2d@crs <- acrs
nov2d@crs <- acrs
dec2d@crs <- acrs

#ratify to categorical
mar2d <- ratify(mar2d)
rat <- levels(mar2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(mar2d) <- rat
apr2d <- ratify(apr2d)
rat <- levels(apr2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(apr2d) <- rat
may2d <- ratify(may2d)
rat <- levels(may2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(may2d) <- rat
jun2d <- ratify(jun2d)
rat <- levels(jun2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(jun2d) <- rat
jul2d <- ratify(jul2d)
rat <- levels(jul2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(jul2d) <- rat
aug2d <- ratify(aug2d)
rat <- levels(aug2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(aug2d) <- rat
sep2d <- ratify(sep2d)
rat <- levels(sep2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(sep2d) <- rat
oct2d <- ratify(oct2d)
rat <- levels(oct2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(oct2d) <- rat
nov2d <- ratify(nov2d)
rat <- levels(nov2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(nov2d) <- rat
dec2d <- ratify(dec2d)
rat <- levels(dec2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(dec2d) <- rat

maplst <- list(mar2d, apr2d, may2d, jun2d, jul2d, aug2d, sep2d, oct2d, nov2d, dec2d)

pstack <- stack(maplst)

# my.at <- seq(0, 1, by = 0.1)
# mapTheme <- infernoTheme(region = rev(inferno(10)))

p <- levelplot(pstack, col.regions=c('white', 'red'), ylab = NULL, xlab = NULL, scales=list(draw=FALSE), layout = c(5, 2), names.attr = c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
plot(p)
```

#probabilty maps (selected)

### 2019-10-16 src/testing_file.Rmd
2d plots finished

my.at <- seq(0, 1, by = 0.1)
mapTheme <- viridisTheme(region = viridis(10), direction = -1)

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(2, 1), names.attr = c("6m", "180m"), margin = FALSE) + layer(sp.polygons(ss, fill = "red")) 
plot(p)

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

>>>>

my.at <- seq(0, 1, by = 0.1)
mapTheme <- infernoTheme(region = rev(inferno(10)))

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(5, 2), names.attr = c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))
plot(p)
